ms_results

### 2024-05-01 ms_results.Rmd
edits on ms results for manuscript archive

```{r load_data}
# Directory
datadir <- "qa/outputs_20240221"

@@

regional_supply_per_cap <- read.csv(file.path(datadir, "fig3b_data.csv"))

@@

foreign_consumption_region <- read.csv(file.path(datadir, "fig3d_data.csv"))

>>>>

```{r load_data}
# Directory
datadir <- "qa/manuscript_archive/manuscript_inputs"

@@

regional_supply_per_cap <- read.csv(file.path(datadir, "fig_4b_data.csv"))

@@

foreign_consumption_region <- read.csv(file.path(datadir, "fig_4d_data.csv"))
